---
title: "Assingment NYC Flight Data"
author: "Shibani Misra"
date: "October 5, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NYC Flight Data

Your job is to create a "rectangular" table useful for modeling from flight data. In the folder `02-fundamentals/data` there are four CSV files: `flights.csv`, `airports.csv`, `planes.csv` and `weather.csv`.  Put code in each of the sections provided.


<!-- install.packages("readr") -->
<!-- install.packages("ggplot2") -->
<!-- install.packages("dplyr") -->
<!-- install.packages("gmodels") -->


## 1. Read Data

Using the `readr` package read the `flights` data.

```{r}
library(readr)
library(ggplot2)
library(dplyr)
library(gmodels)
options(stringsAsFactors = FALSE)
setwd("C:/Users/smisra/tmp/CSX460/02-fundamentals/data")
flights<- read.csv("flights.csv")



```

## Numeric Variables  

Plot a histogram of arrival delays and departure delays 

```{r}
ggplot(flights, aes(x=dep_delay)) +
  geom_histogram(binwidth = 10) +
  coord_cartesian(xlim=c(0, 300))
ggplot(flights, aes(x = arr_delay)) +
  geom_histogram(binwidth = 10) +
  coord_cartesian(xlim=c(0, 300))
```

## Scatterplot

Plot a scatterplot of date vs arrival delay 

```{r}
flights <- flights %>% 
  mutate(flight_date = as.Date(time_hour),
         time_hour1 = as.character(time_hour))

ggplot(flights, aes(x = flight_date, y = arr_delay)) +
  geom_point()

```



## Create tables for Categorical Variables

Create a `table` of occurences of origin airports and carrier.

```{r}
table(flights$origin)
table(flights$carrier)

```


## Join Data

**Read** in the other data sets. Use methods to join the data together to create a single table containing one record per row.  (HINT: see `?data.table` or `?dplyr::join`)

```{r}
airports <- read.csv("airports.csv")
planes <- read.csv("planes.csv")
weather <- read.csv("weather.csv")

flights_wPlaneInfo <- flights %>% 
  left_join(planes, by = c("tailnum")) 


flights_WeatherInfo <- flights_wPlaneInfo %>% 
  left_join(weather, by = c("origin", "time_hour1" = "time_hour")) %>% 
  select(year.x, month.x, day.x, dep_time, sched_dep_time, dep_delay, arr_time, sched_arr_time, arr_delay, carrier, flight, tailnum, origin, dest, distance, hour.x, minute, time_hour, flight_date, type, manufacturer, model, engines, seats, speed, engine, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib)

flights_wOtherInfo <- flights_WeatherInfo %>% 
  left_join(airports, by = c("dest" = "faa"))
write.csv(flights_wOtherInfo, "flightDataWithOtherInfo.csv")
```



