---
title: "NYCFlights: Arrival Delay Logistic Model"
author: "Shibani Misra"
date: "10/24/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(caret)
```


# Logistic and Inverse Logistic Transformation

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.

```{r "Logistic Function" }
getp <- function(y) {
  exp(y)/(1+exp(y))
}
```
- Plot the logistic function from  `[-10,10]`

```{r "Plot logistic function"}
theta_lr <- sample(-10:10, 10, replace=FALSE)

resp.prob <-  as.data.frame(unlist(lapply(theta_lr, getp)))
df <- cbind(as.data.frame(theta_lr),resp.prob)

ggplot(df, aes(x = theta_lr, y = resp.prob)) +
  geom_point(alpha = 0.5)
  
```

- Write a R function for the inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

```{r "R function for inverse logistic function"}
inv_log <- function(p){
  log(p/(1-p))
}
```

- Plot the Inverse Logistic function from `[0,1]`

```{r "Plot inverse logistic function"}
inv_p <- as.data.frame(runif(21))
theta <- as.data.frame(unlist(lapply(inv_p, inv_log)))
df2 <- cbind(inv_p,theta)
ggplot(df2, aes(x = inv_p, y = theta)) + geom_point(alpha = 0.5)

```

**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`

```{r "Logistic and Inverse Logistic" }


```


# NYCFlights Model

Using the rectangular data that you created from assignment and following the *Predicting Medical Expenses* example from the text (*MLwR*), create a model for arr_delay >= 15 minutes. Follow *MLwR* structure   for building a model. Describe/Explain each of the steps and show all work in codeblocks below.

KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file.   

## Step 1: Collect Data 

```{r "Step 1: Collect Data" }
options(stringsAsFactors = FALSE)

flights.mod <- read.csv("C:/Users/smisra/tmp/CSX460/03-linear-regression/flightDataWithOtherInfo.csv")
flights.mod <- flights.mod %>% 
  filter(is.na(arr_delay)== FALSE)

flights.additionalcols <- flights.mod  %>%
mutate(season = ifelse(month.x %in% c(12,1,2), "Winter", ifelse(month.x %in% c(3,4,5), "Spring", ifelse(month.x %in% c(6,7,8), "Summer", "Fall"))), headwind = cos(wind_dir) * wind_speed, 
       wday = weekdays(as.Date(flight_date))) %>% 
mutate(season = as.factor(season), wday = as.factor(wday), headwind = abs(headwind))
trainIndex <- createDataPartition(flights.additionalcols$arr_delay, p = .8, 
                                  list = FALSE, 
                                  times = 1)

flightTrain <- flights.additionalcols[ trainIndex,]
flightTest  <- flights.additionalcols[-trainIndex,]
```

## Step 2: Explore and Prep The Data


One of the things not done in the MLwR text is a pairwise comparison between the response and each of the predictors. Make sure to do this; this is often very illustrative of the relationship between that predictor and the response. This can be done with `pairs` or `psych::panel.pairs`


```{r "Step 2: Explore and Prep The Data" }
flightTrain <- flightTrain %>% 
  mutate(arr_delay_cat = ifelse(arr_delay >=15, 1,0))
flightTest <- flightTest %>% 
  mutate(arr_delay_cat = ifelse(arr_delay >=15, 1, 0))

```

## Step 3:  Train The Model

```{r "Step 3: Train The Model" }
form <- arr_delay_cat ~ dep_delay + wind_gust + season + wday + precip
flights.glm.model <- glm(form, data = flightTrain, family = binomial())
```

## Step 4: Evaluate Performance

Think about some of the tools that you have for evaluating performance.  Choose one and articulate why you have chosen it.

```{r "Step 4: Evaluate Performance" }
summary(flights.glm.model)
arr_delay_cat_pred <- as.data.frame(predict(flights.glm.model, type = "response"))
colnames(arr_delay_cat_pred) <- c("predicted_arr_delay_prob")
threshold = 0.5
arr_delay_cat_pred <- arr_delay_cat_pred %>% 
  mutate(predicted_arr_delay_01 =  ifelse(predicted_arr_delay_prob > 0.5, 1, 0))
flightTrain <- flightTrain %>% 
  filter(is.na(arr_delay) == FALSE)


```

 
## Step 5: Improve Performance 

Show some steps for improving model performance.

```{r "Step 5: Improve Performance" }

```


# Question:

Is this a good model?  (Write your answer here.)

Couldn't check for model performance because for some reason the length of the predicted values 
vector is not matching the actual response value vector.

# PART B:

Your model should be good at explaining tardiness. Now, assume that your job is to predict arrival delays a month in advance. You can no longer use all the features in your model. Retrain your model using only features that will be *known* only a month in advance of the departure time.  Show all steps as above.

```{r "Forecasting Model" }
form2 <- arr_delay_cat ~ season + wday + origin + carrier
flights.glm.model2 <- glm(form2, data = flightTrain, family = binomial())
summary(flights.glm.model2)
```
