---
title: "Classification Metrics"
author: "Shibani Misra"
date: "11/08/2016"
output: html_document
---

<<<<<<< HEAD
The Flights Data ; 

1. Read in the Flights Data
2. Partition the model into Test and Training Sets using only `base::sample` 
3. Train a model for `Creditability` 
4. Knit the document and submit both the this file Rmd and html files.

Show All Work! 
=======
Using the first **logistic regression** model that you created in previous exercise; 

1. Partition the model into Test and Training Sets using only `base::sample` 
>>>>>>> c0e49b99fba8263cda933bb4efffc7dd6b4352e0

```{r}
library(dplyr)
library(e1071)
library(caret)
library(ggplot2)
library(ROCR)
load(file = "flights.Rda")
flights_sample <- flights[sample(nrow(flights), 100000, replace = FALSE),]
flights_sample <- flights_sample %>% 
  mutate(arr_delay_cat = as.factor(arr_delay_cat),
         carrier = as.factor(carrier),
         tailnum = as.factor(tailnum),
         origin = as.factor(origin),
         dest = as.factor(dest), 
         type = as.factor(type),
         manufacturer = as.factor(manufacturer),
         model = as.factor(model),
         engine = as.factor(engine),
         name = as.factor(name))

<<<<<<< HEAD
Repeats <- 100
cv_repeat_num <- Repeats/20

for (j in 0:(cv_repeat_num -1)) {
  cv_group <- sample(1:20, nrow(flights_sample), replace = T)
  for (i in 1:20) {
    flightTrain <- flights_sample[cv_group != i,]
    flightTest <- flights_sample[cv_group == i,]
    form <- arr_delay_cat ~ dep_delay + wind_gust + season + wday + precip  + origin + visib
    flights.my.model <- glm(form, data = na.omit(flightTrain), family = binomial())
    
    predict_step <- predict(flights.my.model, newdata = flightTest, type = "response")
    pred_s <- prediction(predict_step, flightTest$arr_delay_cat)
    auc_s <- performance(pred_s, measure = "auc")
    
    if (i == 1 & j == 0) { results <- c(auc_s = auc_s@y.values[[1]])}
    results <- append(results, c(auc_s = auc_s@y.values[[1]]), after = length(results))
   
  }
}
cv_stat <- mean(results)
print(cv_stat)
threshold = 0.5
flightTest <- flightTest %>% 
    mutate(arr_delay_pred = ifelse(predict_step > 0.5, 1, 0),
           arr_delay_cat = as.factor(arr_delay_cat))
flightTest <- flightTest %>% 
  mutate(TP = ifelse(arr_delay_cat == 1 & arr_delay_pred == 1, 1, 0),
         FP = ifelse(arr_delay_cat == 0 & arr_delay_pred == 1, 1, 0),
         TN = ifelse(arr_delay_cat == 0 & arr_delay_pred == 0, 1, 0), 
         FN = ifelse(arr_delay_cat == 1 & arr_delay_pred == 0, 1, 0))
pred <- predict(flights.my.model, newdata=flightTest, type = "response")
pred <- ifelse(pred > 0.5, 1,0)
accuracy <- table(pred, flightTest[,"arr_delay_cat"])
acc <- sum(diag(accuracy))/sum(accuracy)

confusionMatrix(data=pred, flightTest$arr_delay_cat)

=======
>>>>>>> c0e49b99fba8263cda933bb4efffc7dd6b4352e0
```

2. Re-train the model on the training data 

```{r}

```

3. Using the `predict` function and `test` data, write functions to calculate and 
calculate: 

* Misclassification Rate
* Prevalence 
* Accuracy
* Accuracy
* Error Rate / Misclassification Rate
* True Positive Rate  
* False Positive Rate
* True Negative Rate  
* False Negative Rate 
* Sensitivity 
* Specificity 
* Recall 
* Precision

```{r, echo=FALSE}


```
